MSF_Groupwork-NBA_shotlog

### 2016-10-12 MSFGroupwork-NBAHotHand.Rmd

```{r}
#install.packages('reshape')

### Calling libraries
```{r}
library(reshape)
library(ggplot2)

@@

#Set a new data frame for the 5 players with best performances(higher points)
best_players_df <- head(pttsum2,5)

@@

#Create a data frame for the strikes of each one of the 10 players (cannot create a data frame including all of them, because each list has different length)
player1_df <- data.frame('streaks' = streak_per_player[[1]])
player2_df <- data.frame('streaks' = streak_per_player[[2]])
player3_df <- data.frame('streaks' = streak_per_player[[3]])
player4_df <- data.frame('streaks' = streak_per_player[[4]])
player5_df <- data.frame('streaks' = streak_per_player[[5]])

#Show distribution for each player's streak lengths
ggplot(data = player1_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[1,'player_name'])
ggplot(data = player2_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[2,'player_name'])
ggplot(data = player3_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[3,'player_name'])
ggplot(data = player4_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[4,'player_name'])
ggplot(data = player5_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[5,'player_name'])

#Create a boxplot for each player's streak lengths
boxplot(player1_df$streaks) 
summary(player1_df$streaks) #Check that boxplot is valid
IQR(player1_df$streaks) #Check that boxplot is valid
#The typical length of a streak is 1 (median = 1) - The Interquartile Range is 1 - Streak length of 6 is unusually high compared to the rest of the distribution
boxplot(player2_df$streaks)
summary(player2_df$streaks)
IQR(player2_df$streaks)
#The typical length of a streak is 1.5 (median = 1.5) - The Interquartile Range is 1 - Streak length of 4 is unusually high compared to the rest of the distribution
boxplot(player3_df$streaks)
summary(player3_df$streaks)
IQR(player3_df$streaks)
#The typical length of a streak is 8 (median = 8) - The Interquartile Range is 5 - There is a streak lengths of 13(!!!)
boxplot(player4_df$streaks)
summary(player4_df$streaks)
IQR(player4_df$streaks)
#The typical length of a streak is 2 (median = 2) - The Interquartile Range is 1.5 - Streak length of 6 is unusually high compared to the rest of the distribution
boxplot(player5_df$streaks)
summary(player5_df$streaks)
IQR(player5_df$streaks)
#The typical length of a streak is 2 (median = 2) - The Interquartile Range is 2 - There are some high streak lengths (max = 5)

@@

#Find the shooting percentage for each of the 5 players
j <- 1
shooting_percentage <- list()
for(i in best_players_df$player_id) {
  shooting_percentage[j] <- sum(df[df[ ,'player_id'] == i, 'FGM'])/ nrow(df[df[ ,'player_id'] == i, ])
  j <- j+1
}
shooting_percentage

###PLAYER 1 VS SAMPLE PLAYER###
#Simulation - create a vector of shots('made', 'missed') for a sample shooter, setting as probability the shooting percentage of the real shooter1 
set.seed(21)
shot_results <- c('made', 'missed')
simul_shooter <- sample(shot_results, size = length(streak_per_player[[1]]), replace = TRUE, prob = c(shooting_percentage[[1]], 1 - shooting_percentage[[1]]))
simul_shooter

@@

#Remove zeros
true_streaks_of_simulshooter <- list()
j <- 1
for(i in 1:length(streaks_of_simulshooter)) {
  if(streaks_of_simulshooter[[i]] != 0){
    true_streaks_of_simulshooter[j] <- streaks_of_simulshooter[[i]]
    j <- j + 1
  }
}
true_streaks_of_simulshooter
true_streaks_of_simulshooter <- unlist(true_streaks_of_simulshooter)

#Create a data frame 
simulshooter_df <- data.frame('streaks' = true_streaks_of_simulshooter)
simulshooter_df

#Comparisons of data between sample shooter and real shooters
summary(simulshooter_df$streaks)
summary(player1_df$streaks)

#Compare barplots of sample shooter and real shooter1
#If real shooter's streaks diverge significantly from an independent shooter's streaks(sample shooter's streaks), we can conclude tha the real shooter has a 'hot hand'. 
ggplot(data = simulshooter_df, aes(x = streaks)) + geom_bar() 
ggplot(data = player1_df, aes(x = streaks)) + geom_bar()
#We can see that streak length distributions are quite similar, so we can conclude that Kyrie Irving doesn't have a hot hand.

###PLAYER 2 VS SAMPLE PLAYER###
#Simulation - create a vector of shots('made', 'missed') for a sample shooter, setting as probability the shooting percentage of the real shooter2 
set.seed(154)
shot_results <- c('made', 'missed')
simul_shooter <- sample(shot_results, size = length(streak_per_player[[2]]), replace = TRUE, prob = c(shooting_percentage[[2]], 1 - shooting_percentage[[2]]))
simul_shooter

@@

#Remove zeros
true_streaks_of_simulshooter <- list()
j <- 1
for(i in 1:length(streaks_of_simulshooter)) {
  if(streaks_of_simulshooter[[i]] != 0){
    true_streaks_of_simulshooter[j] <- streaks_of_simulshooter[[i]]
    j <- j + 1
  }
}
true_streaks_of_simulshooter
true_streaks_of_simulshooter <- unlist(true_streaks_of_simulshooter)

#Create a data frame 
simulshooter_df <- data.frame('streaks' = true_streaks_of_simulshooter)

#Comparisons of data between sample shooter and real shooters
summary(simulshooter_df$streaks)
summary(player2_df$streaks)

#Compare barplots of sample shooter and real shooter1
#If real shooter's streaks diverge significantly from an independent shooter's streaks(sample shooter's streaks), we can conclude tha the real shooter has a 'hot hand'. 
ggplot(data = simulshooter_df, aes(x = streaks)) + geom_bar() 
ggplot(data = player2_df, aes(x = streaks)) + geom_bar()
#We can see that the sample shooter with the same shooting percentage can have extremely high streak lengths, which means that Mo Williams does not have a hot hand.

###PLAYER 3###

best_players_df
#logistic regression

>>>>

```{r}
#install.packages('reshape')
#install.packages('gridExtra')
```

### Calling libraries
```{r}
library(reshape)
library(ggplot2)
library(gridExtra)
```

@@

#Set a new data frame for the 3 players with best performances(higher points)
best_players_df <- head(pttsum2,3)

@@

#Create a data frame for the strikes of each one of the 3 players (cannot create a data frame including all of them, because each list has different length)
player1_df <- data.frame('streaks' = streak_per_player[[1]])
player2_df <- data.frame('streaks' = streak_per_player[[2]])
player3_df <- data.frame('streaks' = streak_per_player[[3]])

#Show distribution for each player's streak lengths
gg1 <- ggplot(data = player1_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[1,'player_name'])
gg2 <- ggplot(data = player2_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[2,'player_name'])
gg3 <- ggplot(data = player3_df, aes(x = streaks)) + geom_histogram(binwidth = 1) + labs(title = ourtable[3,'player_name'])
grid.arrange(gg1, gg2, gg3, ncol = 3)

#Create a boxplot for each player's streak lengths
boxplot(player1_df$streaks) 
summary(player1_df$streaks) #Check that boxplot is valid
IQR(player1_df$streaks) #Check that boxplot is valid
#The typical length of a streak is 1 (median = 1) - The Interquartile Range is 1 - Streak length of 6 is unusually high compared to the rest of the distribution
boxplot(player2_df$streaks)
summary(player2_df$streaks)
IQR(player2_df$streaks)
#The typical length of a streak is 1.5 (median = 1.5) - The Interquartile Range is 1 - Streak length of 4 is unusually high compared to the rest of the distribution
boxplot(player3_df$streaks)
summary(player3_df$streaks)
IQR(player3_df$streaks)
#The typical length of a streak is 8 (median = 8) - The Interquartile Range is 5 - There is a streak lengths of 13(!!!)

@@

#Find the shooting percentage for each of the 3 players
j <- 1
shooting_percentage <- list()
for(i in best_players_df$player_id) {
  shooting_percentage[j] <- sum(df[df[ ,'player_id'] == i, 'FGM'])/ nrow(df[df[ ,'player_id'] == i, ])
  j <- j+1
}
shooting_percentage

###PLAYER 1 VS SAMPLE PLAYER###
#Simulation - create a vector of shots('made', 'missed') for a sample shooter, setting as probability the shooting percentage of the real shooter1 
set.seed(974)
shot_results <- c('made', 'missed')
simul_shooter <- sample(shot_results, size = length(streak_per_player[[1]]), replace = TRUE, prob = c(shooting_percentage[[1]], 1 - shooting_percentage[[1]]))
simul_shooter

@@

#Create new data frames for the graphs 
simulshooter_df <- data.frame('streaks' = streaks_of_simulshooter)
realshooter_df <- data.frame('streaks' = streak_per_player[[1]])

#Comparisons of data between sample shooter and real shooters
summary(simulshooter_df$streaks)
summary(realshooter_df$streaks)

#Compare barplots of sample shooter and real shooter1
#If real shooter's streaks diverge significantly from an independent shooter's streaks(sample shooter's streaks), we can conclude tha the real shooter has a 'hot hand'. 
g1 <- ggplot(data = simulshooter_df, aes(x = streaks )) + geom_bar() + labs(title = 'sample shooter')
g2 <- ggplot(data = realshooter_df, aes(x = streaks)) + geom_bar() + labs(title = 'Kyrie Irving')
grid.arrange(g1, g2, ncol = 2)
#We can see that streak length distributions are quite similar, so we can conclude that Kyrie Irving doesn't have a hot hand.

###PLAYER 2 VS SAMPLE PLAYER###
#Simulation - create a vector of shots('made', 'missed') for a sample shooter, setting as probability the shooting percentage of the real shooter1 
set.seed(572)
shot_results <- c('made', 'missed')
simul_shooter <- sample(shot_results, size = length(streak_per_player[[2]]), replace = TRUE, prob = c(shooting_percentage[[2]], 1 - shooting_percentage[[2]]))
simul_shooter

@@

#Create new data frames for the graphs 
simulshooter_df <- data.frame('streaks' = streaks_of_simulshooter)
realshooter_df <- data.frame('streaks' = streak_per_player[[2]])

#Comparisons of data between sample shooter and real shooters
summary(simulshooter_df$streaks)
summary(realshooter_df$streaks)

#Compare barplots of sample shooter and real shooter1
#If real shooter's streaks diverge significantly from an independent shooter's streaks(sample shooter's streaks), we can conclude tha the real shooter has a 'hot hand'. 
g1 <- ggplot(data = simulshooter_df, aes(x = streaks )) + geom_bar() + labs(title = 'sample shooter')
g2 <- ggplot(data = realshooter_df, aes(x = streaks)) + geom_bar() + labs(title = 'Mo Williams')
grid.arrange(g1, g2, ncol = 2)

###PLAYER 3 VS SAMPLE PLAYER###
#Simulation - create a vector of shots('made', 'missed') for a sample shooter, setting as probability the shooting percentage of the real shooter1 
set.seed(57)
shot_results <- c('made', 'missed')
simul_shooter <- sample(shot_results, size = length(streak_per_player[[3]]), replace = TRUE, prob = c(shooting_percentage[[3]], 1 - shooting_percentage[[3]]))
simul_shooter

#Create new data frames for the graphs 
simulshooter_df <- data.frame('streaks' = streaks_of_simulshooter)
realshooter_df <- data.frame('streaks' = streak_per_player[[3]])

#Comparisons of data between sample shooter and real shooters
summary(simulshooter_df$streaks)
summary(realshooter_df$streaks)

#Compare barplots of sample shooter and real shooter1
#If real shooter's streaks diverge significantly from an independent shooter's streaks(sample shooter's streaks), we can conclude tha the real shooter has a 'hot hand'. 
g1 <- ggplot(data = simulshooter_df, aes(x = streaks )) + geom_bar() + labs(title = 'sample shooter')
g2 <- ggplot(data = realshooter_df, aes(x = streaks)) + geom_bar() + labs(title = 'Klay Thompson')
grid.arrange(g1, g2, ncol = 2)
#Klay Thompson is an exception, had 13 streaks in a row! We cannot find a similar distribution in our sample, so we can assume that he is likely to have a hot hand.

best_players_df
